Comparison with Christensen paper

### 2019-01-17 paper-comparison/compare-christensen.Rmd
Adding ldats lda adjusted/nonadjusted data comparisons
Correct rodents to rodents_adj in second half of vignette
The model objects referenced past the lda with adjusted/nonadjusted comparison were generated using the adjusted data, which I renamed to rodents_adjusted when I did the adj/nonadj comparison. Rather than rerun things, for now I am renaming the object later in the narrative for consistency.

paper_gamma_comparison <- ldamodel_adj@gamma == ldamodel_nonadj@gamma
unique(paper_gamma_comparison)

@@

ldats_ldas <- LDATS::LDA_set(document_term_table = rodents$document_term_table, topics = c(2:6), nseeds = 100)
ldats_lda_selected <- LDATS::select_LDA(LDA_models = ldats_ldas)

@@

# ==================================================================
# 3. run LDA model
# ==================================================================
ntopics = 4
SEED = unlist(best_seed)[1]  # For the paper, I use seed 206
ldamodel = LDA(rodents[[1]],ntopics, control = list(seed = SEED),method='VEM')

>>>>

```{r ldats adj lda}
load('~/Dropbox/ldats-models/ldats_lda_adj_data.Rds')

plot(ldats_adj_lda_selected[[1]])

ldats_adj_lda_selected[[1]]@k

```{r ldats nonadj lda}
load('~/Dropbox/ldats-models/ldats_lda_nonadj_data.Rds')

plot(ldats_nonadj_lda_selected[[1]])

ldats_nonadj_lda_selected[[1]]@k

@@

ldats_ldas <- LDATS::LDA_set(document_term_table = rodents_adj$document_term_table, topics = c(2:6), nseeds = 100)
ldats_lda_selected <- LDATS::select_LDA(LDA_models = ldats_ldas)

@@

# ==================================================================
# 3. run LDA model
# ==================================================================
ntopics = 4
SEED = unlist(best_seed)[1]  # For the paper, I use seed 206
ldamodel = LDA(rodents_adj[[1]],ntopics, control = list(seed = SEED),method='VEM')
